Report

### 2023-07-07 script/report.Rmd
update report

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE , warning=FALSE, error=FALSE, message=FALSE, out.width="70%", fig.show="hold")
```

@@

```{r}
#libraries
library(DT)
library(ggplot2)
library(vcfR)
library(dplyr)
library(tidyr)
library(yaml)
library(stringr)
library(ComplexHeatmap)
library(dendextend) 
library(GenomicRanges)
library(gplots)
source("functions.R")
```

@@

# Small variant calling step (GATK)
```{r}
vcf.file <- paste0(workspace,"/03_snv_indels_calling/", projectName , "_snv_indel.vcf")
if(!file.exists(vcf.file)) stop("Error: ")
```

>>>>

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE , warning=FALSE, error=FALSE, message=FALSE, out.width="70%", fig.show="hold", eval = FALSE)
```

```{r}
#libraries
library(DT)
library(ggplot2)
library(vcfR)
library(dplyr)
library(tidyr)
library(stringr)
library(dendextend) 
#library(GenomicRanges)
source("functions.R")
```

@@

# Small variant calling step (GATK)
```{r}
vcf.file <- list.files(path = paste0(workspace,"/03_snv_indels_calling"), pattern = "_snv_indel.vcf" , full.names = T)
if(!file.exists(vcf.file)) stop("Error: ")
```
